Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
set seed

## Models 
```{r Linear Regression}
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ lat + lon + state)

@@

```{r kNN}
# Find ideal k neighbors
sqrt(nrow(train))

@@

# Fit the model on the full training dataset using the `fit()` function
res2 <- fit(wf2, data = train_scaled)

@@

```{r Boost}
# Preprocessing "recipe"
preprocessing_recipe <- 
  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
  # Convert categorical variables to factors
  recipes::step_string2factor(all_nominal()) %>%
  # Combine low frequency factor levels
  recipes::step_other(all_nominal(), threshold = 0.01) %>%
  # Remove no variance predictors which provide no predictive information 
  recipes::step_nzv(all_nominal()) %>%
  prep()

@@

@@

train_prediction <- xgboost_model_final %>%
  # Fit the model on all the training data
  fit(formula = value ~ lon+lat, data = train_processed) %>%
  # Predict the sale prices for the training data
  predict(new_data = train_processed) %>%
  bind_cols(training(ames_split))

xgboost_score_train <- train_prediction %>%
  yardstick::metrics(sale_price, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
knitr::kable(xgboost_score_train)
```

```{r Bootstrap}
# Create Bootstrap Model (resampling data)
set.seed(123)
model3 <- boost_tree() %>% 
    set_engine("xgboost") %>%
    set_mode("regression")

@@

```{r Random Forest}
# Create Random Forest Model
set.seed(123)
# Use grid of tuning parameters
model4 <- rand_forest(mtry = tune("mtry"),
                     min_n = tune("min_n")) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")
# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)

>>>>

## Models 
```{r Linear Regression}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ lat + lon + state)

@@

```{r kNN}
set.seed(123)
# Find ideal k neighbors
sqrt(nrow(train))

@@

# Fit the model on the training dataset using the `fit()` function
res2 <- fit(wf2, data = train_scaled)

@@

```{r Boost}
set.seed(123)
# Preprocessing "recipe"
preprocessing_recipe <- 
  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
  # Convert categorical variables to factors
  recipes::step_string2factor(all_nominal()) %>%
  # Combine low frequency factor levels
  recipes::step_other(all_nominal(), threshold = 0.01) %>%
  # Remove no variance predictors which provide no predictive information 
  recipes::step_nzv(all_nominal()) %>%
  prep()

@@

res3 = xgboost_model_final %>% fit(formula = value ~ lon+lat, data = train)
  extract_fit_engine() %>% 
  summary()

folds3 <- vfold_cv(train, v = 10)
# folds
res3 <- fit_resamples(wf3, resamples = folds3) 
res3 %>% 
    collect_metrics()

@@

train_prediction <- xgboost_model_final %>%
  # Fit the model on all the training data
  fit(formula = value ~ lon+lat, data = train_processed) %>%
  # Predict the sale prices for the training data
  predict(new_data = train_processed) %>%
  bind_cols(training(dat_split))

xgboost_score_train <- train_prediction %>%
  yardstick::metrics(value, .pred) %>%
  mutate(.estimate = format(round(.estimate, 2), big.mark = ","))
knitr::kable(xgboost_score_train)
```

```{r Bootstrap}
set.seed(123)
# Create Bootstrap Model (resampling data)
set.seed(123)
model3 <- boost_tree() %>% 
    set_engine("xgboost") %>%
    set_mode("regression")

@@

```{r Random Forest}
set.seed(123)
# Create Random Forest Model
set.seed(123)
# Use grid of tuning parameters
model4 <- rand_forest(mtry = tune("mtry"),
                     min_n = tune("min_n")) %>% 
    set_engine("ranger") %>% 
    set_mode("regression")
# Create workflow
  wf4 <- workflow() %>% 
    add_recipe(rec) %>% 
    add_model(model4)
